Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-11-30 paper/sec-intro.tex
more work on paper

In this work, we revisit the feasibility of SM Higgs pair production by gluon-fusion
in the $b\bar{b}b\bar{b}$ final state.
%
 Our strategy is based on a combination of traditional cut-based
 methods with modern multivariate analysis (MVA),
 leading to a substantial
  enhancement of the signal discrimination.
  %
  We account for  all relevant
  backgrounds, including the contribution from light jet fakes.
  %
  We also model the impact of the pile-up (PU) effects expected at the
  HL-LHC by means of modern PU subtraction techniques.
  %
  By combining the contribution from the boosted, intermediate and resolved
  topologies we achieve a total signal significance of $S/\sqrt{B}\simeq 4.0$
  for $\mathcal{L}_{\rm int}$=3000 fb$^{-1}$.
%
  These results emphasize the crucial importance that the $b\bar{b}b\bar{b}$ final state
  has for studies of Higgs pair production and for the determination of
  $\lambda$, as well as the advantages of the use of modern statistical
  analysis methods.

>>>>

In this work, we revisit the feasibility of SM Higgs pair production by gluon-fusion
in the $b\bar{b}b\bar{b}$ final state.
%
 Our strategy is based on a combination of traditional cut-based
 methods with modern multivariate analysis (MVA),
 leading to a substantial
  enhancement of the signal discrimination.
  %
  We account for  all relevant
  backgrounds, including the contribution from light jet fakes.
  %
  We also model the impact of the pile-up (PU) effects expected at the
  HL-LHC by means of modern PU subtraction techniques,
  in particular the {\tt SoftKiller} method~\cite{Cacciari:2014gra}.
  %
  By combining the contribution from the boosted, intermediate and resolved
  topologies we achieve a total signal significance of $S/\sqrt{B}\simeq 4.0$
  for $\mathcal{L}_{\rm int}$=3000 fb$^{-1}$.
%
  These results emphasize the crucial importance that the $b\bar{b}b\bar{b}$ final state
  has for studies of Higgs pair production and for the determination of
  $\lambda$, as well as the advantages of the use of modern statistical
  analysis methods.

### 2015-11-30 paper/sec-mcsamples.tex
more work on paper

First of all in this section we discuss the settings of the
Monte Carlo generation of the signal and background
events used in this work.
%
We also discuss how we study the effects of finite detector
resolution by means of an smearing of the final-state
particles four-momentum.

\subsection{Higgs pair production}
%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Higgs pair production is simulated at leading order using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
%
We use a tailored {\tt MadGraph5\_aMC@NLO} model~\cite{Maltoni:2014eza} that simulates
gluon-gluon-fusion Higgs boson pair production including the effects
of the
exact form factors for the top triangle and box loops at leading
order, the latter taken from from~\cite{Plehn:1996wb}.\footnote{We note that since recently it is possible to compute also
loop-induced processes in {\tt MadGraph5\_aMC@NLO} without the need of using specific
models~\cite{Hirschi:2015iia}.}
%
We adopt the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
$\alpha_S(m_Z^2)=0.118$
as interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.
%
We use the default settings of the renormalization and factorization
scale of the model.
%
The Higgs boson parameters are also the same in the default model,
in particular we use $m_h=125$ GeV, consistent with the latest
measurements from ATLAS and CMS~\cite{Aad:2014aba,Khachatryan:2014jba}.
%
The value of the Higgs trilinear coupling $\lambda$ is set to its
Standard Model value.
%
The calculation is performed in the
$N_f$=4 scheme and thus
takes into account the finite mass of the $b$-quarks.

In Fig.~\ref{fig:hhFeyn} we show representative Feynman diagrams
    for Higgs pair production in gluon fusion at
    leading order.
    %
    The non-trivial interplay between the diagram with a heavy quark box
    and that of the triangle (that can lead to constructive or destructive interference)
    complicated the extraction of
    the trilinear coupling
    $\lambda$ from the measurement of the Higgs pair
    production cross-section.

The resummed NNLO+NNLL calculations for Higgs pair production have become available recently~\cite{deFlorian:2015moa},
leading to a moderate enhancement of the order of
few percent as compared to the fixed-order NNLO calculation.
%
Therefore, to achieve the correct higher-order value of the  integrated cross-section,
we rescale our signal sample using the
NNLO inclusive calculation from Ref.~\cite{deFlorian:2013jea} accounting the threshold resummed
NNLL effects, which corresponds to using a $K$-factor $\sigma_{\rm NNLO+NNLL}/\sigma_{\rm LO}=2.4$, as indicated
in Table~\ref{tab:samples}.

%
Parton level events are then showered with the {\tt Pythia8} Monte
Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea}, in particular with {\tt v8.201}.
%
We use the default settings in the parton shower, in particular
we use the Monash 2013 tune~\cite{Skands:2014pea}, based on the NNPDF2.3LO PDF set~\cite{Ball:2012cx}.
%
We have switched off hadronisation, since this allows a more transparent modeling of
$b$-tagging.
%
A complete simulation of $b$-tagging at the hadron level is difficult to achieve without a full
detector simulator, which is beyond the scope of this paper.
%
For a similar reason, we don't consider underlying event, multiple parton interactions and
pile-up, which can be taken of using a variety of subtraction methods~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba}.
%
The same applies to the background samples, which we discuss now.

@@

Now we turn to discuss the Monte Carlo generation of the relevant background processes.
%
All background samples are generated at leading-order
with the {\tt SHERPA} event generator~\cite{Gleisberg:2008ta}, v2.1.1.
%
As in the case of the signal generation, the NNPDF 3.0 $n_f = 4$ LO set with strong coupling
$\alpha_S(m_Z^2)=0.118$ is used for all samples.
%
Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$ for all
the samples.

We have considered the most relevant background
processes that can lead to an event
being tagged as a $hh\to 4b$ candidate.
%
First of all we have QCD $4b$ multi-jet production of course, but
we also generate QCD $2b2j$ and $4j$ multi-jet samples,
that can lead to the event being tagged in the case of multiple light
jets being mistagged as $b$-quarks.
%
While the light jet mistag probability is small, we find that
in general the $2b2j$ and $4j$ backgrounds cannot be neglected because
of their large cross-sections and enhancement from combinatorics, that
increase their contribution as compared to a naive estimate.
%
In addition, we find that there is an important contribution from the radiation
of $b$-quarks off light partons during the parton shower, which enhances the contribution
of parton-level $2b2j$ and $4j$ events being tagged as signal events.
%
Neglecting the  $2b2j$ and $4j$ backgrounds is particularly
important for the resolved and intermediate categories, but less
so for the boosted one.

In addition to the QCD multijet, we also generate $t\bar{t}$ samples
in the fully hadronic final state, which lead to a $2b4j$ signature that can
contribute to the fake rates, and that has a similar topology that
the corresponding QCD sample.
%
We have used a value of the top quark mass of $m_t=173.2$ GeV.
%
Semileptonic decays of top quarks can be easily removed by requiring
a lepton veto.

The LO cross-section of the background samples has been rescaled so that the integrated
distributions reproduce known higher-order QCD results.
%
For the $4b$ and $2b2j$ samples, a NLO/LO $K$-factor has been determined
using {\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}, which turns out to be 1.6 and 1.3
respectively.
%
For the $4j$ sample, we rescale it using the {\tt BLACKHAT}~\cite{Bern:2011ep}
results that indicates
a NLO/LO $K$-factor of 0.6.
%
Finally, the LO cross-section for $t\bar{t}$ production has been rescaled
to match the NNLO+NNLL calculation of Ref.~\cite{Czakon:2013goa}, which leads
to a $K$-factor of 1.4.
%
The $K$-factors that we use to rescale all the background samples have been collected in
Table~\ref{tab:samples}.

At the generation level the following basic cuts are applied to
background events.
%
Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located
in the central region with
$| \eta | \le 3.0$.
%
In addition, at the matrix element level
all final state particles must be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
%
We have checked that the generator-level cuts are loose enough as compared to the actual
analysis cuts.
%

Total cross-sections and details of the samples generated are shown in Table~\ref{tab:samples}.
%
First of all we see that the $t\bar{t}$ and QCD $4b$ samples are of
the same order of magnitude.
%
The $bbjj$ cross-section is more than a factor 200 as compared to the
$4b$ result, so in principle it should be subleading taking into
account the mistag rate, but as we will show below,
this is not true due both to combinatorics and to $b$-quark radiation
during the parton shower.
%
 For top quark production, only the hadronic final state is generated.
 %
 We also provide in each case the corresponding inclusive $K$-factor
  that is applied in each case to correctly normalize the distribution to the known
  higher-order results.

%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{LO}}$ (pb)  & $K$-factor \\
\hline
\hline
$pp \to hh$ &  {\tt MadGraph5\_aMC@NLO} & 100K & $1.71\times10^{-2}$  &  2.4  (NNLO+NNLL~\cite{deFlorian:2013jea,deFlorian:2015moa}) \\
\hline
\hline
$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA}v2.1.1 & 3M &$1.12 \times10^3$  & 1.6 (NLO~\cite{Alwall:2014hca}) \\
$pp \to b\bar{b}jj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.66 \times 10^5$ & 1.3 (NLO~\cite{Alwall:2014hca}) \\
$pp \to jjjj$ &  {\tt SHERPA}v2.1.1 & 3M  & $9.71\times 10^6$ &  0.6 (NLO~\cite{Bern:2011ep})\\
$pp \to t\bar{t}\to b\bar{b}jjjj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.51\times 10^3$   & 1.4 (NNLO+NNLL~\cite{Czakon:2013goa})\\
\hline
\end{tabular}
\caption{\small Summary of signal and background samples generated,
  together with the corresponding generator-level LO cross-sections.
  %
  For top quark production, only the hadronic final state is generated.
  %
We also provide in each case the corresponding inclusive $K$-factor
  that is applied in each case to correctly normalize the distribution to the known
  higher-order results. \label{tab:samples}
} 
\end{center}
\end{table}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

As a cross-check of the {\tt SHERPA}
background cross-sections reported in Table~\ref{tab:samples}, we have produced leading order
multi-jet samples
using the {\tt MadGraph5\_aMC@NLO} program, and compared with the results for the same processes reported in
Ref.~\cite{Alwall:2014hca}.
%
For comparison with the latter numbers, 
we require in all samples four anti-$k_T$ $R=0.5$ jets with $p_T \ge 80 $ GeV, and the leading jet must have $p_T \ge 100$ GeV, and
also that all jets must be within an acceptance of $|\eta| \le 2.5 $.
%
We find agreement, within the scale uncertainties, between the {\tt MadGraph5\_aMC@NLO} and {\tt SHERPA} calculations of the multi-jet
backgrounds, so we can be confident that the set-up that we will use in this analysis is robust enough.

Finally, let us discuss the smearing applied to signal
and background samples.
%
It is beyond the scope of this work to perform a complete study of the impact of
detector effects in this process.
%
However, it is still important to include some form of rough estimate of detector
effects in the analysis, to properly estimate for example the impact
of the Higgs mass window cuts.
%
In this work we simulate the finite momentum resolution of the ATLAS and CMS
hadronic calorimeters by applying a Gaussian smearing to the four components
of the four-momentum $p$, with mean zero and standard deviation $\Delta p$.
%
We take as baseline value a smearing of $\Delta p=5\%$, and in
Sect.~\ref{sec:optimisation} we explore how our results change
if a more optimistic or pessimistic value is assumed for the momentum
resolution in the LHC detectors.

>>>>

In this section we discuss the settings of the
Monte Carlo generation of the signal and background
processes used in this analysis.
%
We also discuss the modelling of finite detector
resolution effects by means of an smearing of the final-state
particles four-momenta.

\subsection{Higgs pair production in gluon-fusion}

@@

Higgs pair production is simulated at leading order using
{\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}.
%
We use a tailored {\tt MadGraph5\_aMC@NLO} model~\cite{Maltoni:2014eza} that simulates
gluon-gluon-fusion Higgs boson pair production including the effects
of the
exact form factors for the top triangle and box loops at leading
order, the latter taken from from~\cite{Plehn:1996wb}.\footnote{We note that since recently it is possible to compute also
loop-induced processes in {\tt MadGraph5\_aMC@NLO} without the need of using specific
models~\cite{Hirschi:2015iia}.}
%
We use the default settings of the renormalization and factorization
scale of the model.
%
The Higgs boson parameters are also the same in the default model,
in particular we use $m_h=125$ GeV, consistent with the latest
measurements from ATLAS and CMS~\cite{Aad:2014aba,Khachatryan:2014jba}.
%
The value of the Higgs trilinear coupling $\lambda$ is set to its
Standard Model value.
%
The calculation is performed in the
$n_f$=4 scheme and thus
takes into account the finite mass of the $b$-quarks.
%
For the input parton distribution functions, we 
adopt the NNPDF 3.0 $n_f = 4$ LO set~\cite{Ball:2014uwa} with
$\alpha_s(m_Z^2)=0.118$
interfaced via {\tt LHAPDF6}~\cite{Buckley:2014ana}.

In Fig.~\ref{fig:hhFeyn} we show representative Feynman diagrams
    for Higgs pair production in gluon fusion at
    leading order.
    %
    The non-trivial interplay between the diagram with a heavy quark box
    and that of the triangle, that can lead to constructive or destructive interference,
    complicates the extraction of
    the trilinear coupling
    $\lambda$ from the measurement of the Higgs pair
    production cross-section.
    %
    Higher order corrections are dominated by gluon radiation
    from either the initial state gluons or from the heavy quark loops.

    The total inclusive cross-section for this processes is
    known up to NNLO~\cite{deFlorian:2013jea}.
    %
Resummed NNLO+NNLL calculations for Higgs pair production have become available recently~\cite{deFlorian:2015moa},
leading to a moderate enhancement of the order of
few percent as compared to the fixed-order NNLO calculation.
%
Therefore, to achieve the correct higher-order value of the  integrated cross-section, we rescale our LO signal sample to match the
NNLO+NNLO inclusive cross-section.
%
This corresponds to using a $K$-factor $\sigma_{\rm NNLO+NNLL}/\sigma_{\rm LO}=2.4$, as indicated
in Table~\ref{tab:samples}.

%
Parton level signal events are then showered with the {\tt Pythia8} Monte
Carlo~\cite{Sjostrand:2007gs,Sjostrand:2014zea} version {\tt v8.201}.
%
We use the default settings for the modeling
of the underlying event (UE), multiple parton
interactions (MPI) and pile-up, by means
of the the Monash 2013 tune~\cite{Skands:2014pea},
with the NNPDF2.3LO PDF set~\cite{Ball:2012cx}.
%
We switched off hadronisation, since this allows a more transparent
modeling of our strategy for
$b$-tagging.
%
A complete simulation of $b$-tagging at the hadron level is difficult
to achieve without a full
detector simulator, which is beyond the scope of this work.

@@

Now we turn to discuss the Monte Carlo generation of the relevant background processes.
%
All background samples are generated at leading-order
with the {\tt SHERPA} event generator~\cite{Gleisberg:2008ta}, {\tt v2.1.1}.
%
As in the case of the signal generation,
the NNPDF 3.0 $n_f = 4$ LO set with strong coupling
$\alpha_s(m_Z^2)=0.118$ is used for all samples.
%
Factorisation and renormalisation scales are set as $\mu_F=\mu_R=H_T/2$ for all
the background processes.

We consider the most relevant background
processes that contribute to the identification of
 $hh\to 4b$ candidate events.
%
This includes  QCD $4b$ multi-jet production, as well as
QCD $2b2j$ and $4j$ multi-jet samples.
%
The latter can lead to the event being identified
as signal in the case of light or charm
jets being mistagged as $b$-jets.
%
While the light jet mistag probability is small, we find that
in general the $2b2j$ and $4j$ backgrounds cannot be neglected because
of their large cross-sections and enhancement from combinatorics, that
increase their contribution as compared to a naive estimate.
%
In addition, we find that there is an important contribution from the radiation
of $b$-quarks off light partons during the parton shower, which enhances the contribution
of parton-level $2b2j$ and $4j$ events being tagged as signal events.
%

In addition to the QCD multijet processes,
we also generate $t\bar{t}$ samples
in the fully hadronic final state, which lead to a
$2b4j$ signature that can
contribute due to light jet mistags.
%
This background processes leads a similar topology that
the corresponding QCD sample.
%
In this case,
we have used a value of the top quark mass of $m_t=173.2$ GeV.
%
Leptonic decays of top quarks can be removed by requiring
a lepton veto, and thus are not included here.

The LO cross-sections for
the background samples have been rescaled so that the integrated
distributions reproduce known higher-order QCD results.
%
For the $4b$ and $2b2j$ samples, a NLO/LO $K$-factor has been determined
using {\tt MadGraph5\_aMC@NLO}~\cite{Alwall:2014hca}, which turns out to be 1.6 and 1.3
respectively.
%
For the $4j$ sample, we rescale it using the {\tt BLACKHAT}~\cite{Bern:2011ep}
results, that indicate
a NLO/LO $K$-factor of 0.6.
%
Finally, the LO cross-section for $t\bar{t}$ production has been rescaled
to match the NNLO+NNLL calculation of Ref.~\cite{Czakon:2013goa}, which leads
to a $K$-factor of 1.4.
%
The $K$-factors that we use to rescale all the background samples have been collected in
Table~\ref{tab:samples}.

At the generation level, the following mild
cuts are applied to
background events.
%
Each final state particle in the hard process must have $p_T \ge 20$ GeV, and be located
in the central  rapidity
region with
$| \eta | \le 3.0$.
%
In addition, at the matrix-element level
all final state particles must be separated by a minimum $\Delta R_{\mathrm{min}} =0.1$.
%
We have checked that the generator-level cuts are loose enough to have
no influence over the analysis cuts.
%

The LO cross-sections,
number of generated events and the higher-order $K$-factors
applied to the signal and background
samples are collected in Table~\ref{tab:samples}.
%
We see that the $t\bar{t}$ and QCD $4b$ samples are of
the same order of magnitude, however, the former can be efficiently
reduced by using top quark reconstruction criteria.
%
The $bbjj$ cross-section is around factor 200 as compared to the
$4b$ result, however, as we will show,
due both to combinatorics and to $b$-quark radiation
during the parton shower it can be comparable or larger
than the irreducible QCD background.
%
 For top quark production, only the hadronic final state is generated.
 %

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Process &  Generator & $N_{\mathrm{evt}}$ & $\sigma_{\mathrm{LO}}$ (pb)  & $K$-factor \\
\hline
\hline
$pp \to hh$ &  {\tt MadGraph5\_aMC@NLO} & 100K & $1.71\times10^{-2}$  &  2.4  (NNLO+NNLL~\cite{deFlorian:2013jea,deFlorian:2015moa}) \\
\hline
\hline
$pp \to b\bar{b}b\bar{b}$ &  {\tt SHERPA}v2.1.1 & 3M &$1.12 \times10^3$  & 1.6 (NLO~\cite{Alwall:2014hca}) \\
$pp \to b\bar{b}jj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.66 \times 10^5$ & 1.3 (NLO~\cite{Alwall:2014hca}) \\
$pp \to jjjj$ &  {\tt SHERPA}v2.1.1 & 3M  & $9.71\times 10^6$ &  0.6 (NLO~\cite{Bern:2011ep})\\
$pp \to t\bar{t}\to b\bar{b}jjjj$ &  {\tt SHERPA}v2.1.1 & 3M & $2.51\times 10^3$   & 1.4 (NNLO+NNLL~\cite{Czakon:2013goa})\\
\hline
\end{tabular}
\caption{\small Details of the signal and background Monte
  Carlo samples generated,
  together with the corresponding generator-level LO cross-sections.
  %
  For top quark production, only the hadronic final state is generated.
  %
We also provide in each case the corresponding inclusive $K$-factor
  that is applied in each case to correctly normalize the distribution to the known
  higher-order results. \label{tab:samples}
} 
\end{center}
\end{table}%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

As a cross-check of the {\tt SHERPA}
background cross-sections reported in Table~\ref{tab:samples}, we have produced leading-order
multi-jet samples
using {\tt MadGraph5\_aMC@NLO}, and
benchmarked them with the results for the same processes reported in
Ref.~\cite{Alwall:2014hca}.
%
For comparison with the latter numbers, 
we require in all samples four anti-$k_T$ $R=0.5$ jets with $p_T \ge 80 $ GeV, and the leading jet must have $p_T \ge 100$ GeV, and
also that all jets must be within an acceptance of $|\eta| \le 2.5 $.
%
We find good agreement, within the scale uncertainties, between the {\tt MadGraph5\_aMC@NLO} and {\tt SHERPA} calculations of the multi-jet
backgrounds.

\subsection{Modelling of detector resolution}

While it is beyond the scope of this work to perform a full
detector simulation, it is still important to include an estimate of detector
effects in the analysis, in particular for the finite resolution
in energy and momentum, which will affect some kinematical variables, in particular
the invariant mass of the Higgs candidates.
%
For example, in the absence of any four-momentum smearing, the impact of the $m_h$
distributions of the Higgs candidates in the MVA
would be unrealistically large.

In this work, we simulate the finite momentum resolution of the ATLAS and CMS
hadronic calorimeters by applying a Gaussian smearing of the transverse
momentum $p_T$ of all
final-state particles, before jet clustering,
with mean zero and standard deviation $\sigma_E$, that is
%
\be
\label{eq:smearing}
p_T^{(i)} \, \to \, p_T^{(i)\prime}= \lp 1+ r_i\cdot\sigma_E \rp\, p_T^{(i)} \, , \quad
i=1,\ldots,N_{\rm part} \, ,
\ee
with $r_i$ an univariate Gaussian random number, different for each
of the $N_{\rm part}$ particles in the event.
%
We take as baseline value a momentum smearing
factor of $\sigma_E=5\%$.
%

To account for the finite angular resolution of the calorimeter,
the $\eta$-$\phi$ plane is divided into regions of
$\Delta \eta \times \Delta \phi=0.1$, and each final state particle
which falls in each of these cells is set of have the same $\eta$
and $\phi$ values of the center of the cell.
%
Finally, the particle's energy is recalculated from the smeared $p_T^\prime$,
$\eta^\prime$ and $\phi^\prime$ values to satisfy the mass-shell
condition.

Our modelling of detector simulation has been motivated
to lead to a mass resolution of
reconstructed Higgs candidates of around 10 GeV, consistent
with the hadronic mass resolutions of ATLAS and CMS.
%
In  Fig.~\ref{fig:higgs-mass-resolution} we show the
invariant mass distributions of the leading
Higgs candidate in signal events for the
resolved category (see Sects.~\ref{sec:analysis}
and~\ref{sec:results}), together with
a Gaussian fit,
used to determine the mass resolution.
%
We indeed  find a mass resolution of about 8\%, corresponding
    to around 10 GeV for $m_H=125$ GeV.
%
    For completeness, in Fig.~\ref{fig:higgs-mass-resolution}
    we also show the corresponding
    mass distributions of Higgs candidates
    in the case of $\la n_{\rm PU}\ra=80$ PU events
    subtracted with {\tt SoftKiller} (see Sect.~\ref{sec:pileup}).
    %
    In the case of PU, the mass resolution is increased to around 11\%, corresponding to
    14 GeV.
    %

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
    \vspace{-1cm}
  \includegraphics[width=0.49\textwidth]{plots/higgs_mass_res_noPU.pdf}
  \includegraphics[width=0.49\textwidth]{plots/higgs_mass_res_PU80.pdf}
  \caption{\small The invariant mass distributions of the leading
    Higgs candidates in signal events for the resolved category, without
    PU (left plot) and with PU (right plot),
    together with Gaussian fits  used to determine the mass resolution.
    %
    In the latter case, $\la n_{\rm PU}\ra=80$, with {\tt SoftKiller}
     used for PU subtraction.
}
\label{fig:higgs-mass-resolution}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
